---
title: "Codebook"
output: github_document
---

```{r setup, include = FALSE}

data_tidy <- read.csv("samsung_wearable_tidy.csv", check.names = FALSE)

```

```{r generate codebook, include = FALSE}

attr(data_tidy, "classes") <- unlist(lapply(data_tidy, function(x) class(x)), use.names = FALSE)

attr(data_tidy, "minimum") <- unlist(lapply(data_tidy, 
                                            function(x) {
                                                if(is.double(x)) {
                                                round(min(x), 2)
                                                } else if(is.integer(x)) {
                                                format(min(x), digits = 0)
                                                } else NA}),
                                     use.names = FALSE)

attr(data_tidy, "maximum") <- unlist(lapply(data_tidy, 
                                            function(x) {
                                                if(is.double(x)) {
                                                round(max(x), 2)
                                                } else if(is.integer(x)) {
                                                format(max(x), digits = 0)
                                                } else NA}),
                                     use.names = FALSE) 
                                            
attr(data_tidy, "na_count") <- unlist(lapply(data_tidy, function(x) sum(is.na(x))), use.names = FALSE)

#attr(data_tidy, "description") <- c("ID of the participating subjects",
#                                    "Activity during measurement: ")


```

### Feature description

The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals t-acc_xyz and t-gyro_xyz. These time domain signals (prefix 't' to denote time) were captured at a constant rate of 50 Hz. Then they were filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz to remove noise. Similarly, the acceleration signal was then separated into body and gravity acceleration signals (t_body_acc_xyz and t_gravity_acc_xyz) using another low pass Butterworth filter with a corner frequency of 0.3 Hz. 

Subsequently, the body linear acceleration and angular velocity were derived in time to obtain Jerk signals (t-body_acc_jerk_xyz and t-body_gyro_jerk_xyz). Also the magnitude of these three-dimensional signals were calculated using the Euclidean norm (t-body_acc_mag, t-gravity_acc_mag, t-body_acc_jerk_mag, t-body_gyro_mag, t-body_gyro_jerk_mag). 

Finally a Fast Fourier Transform (FFT) was applied to some of these signals producing f-body_acc_xyz, f-body_acc_jerk_xyz, f-body_gyro_xyz, f-body_acc_jerk_mag, f-body_gyro_mag, f-body_gyro_jerk_mag. (Note the 'f' to indicate frequency domain signals). 

These signals were used to estimate variables of the feature vector for each pattern: '_xyz' is used to denote 3-axial signals in the X, Y and Z directions.

The set of variables that were estimated from these signals are:

- mean: Mean value
- std: Standard deviation


Additional vectors obtained by averaging the signals in a signal window sample:

- t-body_acc_mag_mean              
- t-gravity_acc_mag_mean    
- t-body_acc_jerk_mag_mean 
- t-body_gyro_mag_mean       
- t-body_gyro_jerk_mag_mean     
- f-body_acc_mag_mean      
- f-body_body_acc_jerk_mag_mean
- f-body_body_gyro_mag_mean
- f-body_body_gyro_jerk_mag_mean


The column subject contains the ID of the person who was wearing the wearable and did the different activities.

The column activity contains information about the activities during the respective measurement: LAYING, SITTING, STANDING, WALKING, WALKING_DOWNSTAIRS, WALKING_UPSTAIRS.



### Dataset attributes

No. of rows: `r {nrow(data_tidy)}`
\
No. of columns: `r {ncol(data_tidy)}`

```{r pressure, echo = FALSE, results = 'asis'}
library(knitr)

kable(data.frame("Variable" = attributes(data_tidy)$names,
                 "Class" = attributes(data_tidy)$classes,
                 "Minimum" = attributes(data_tidy)$minimum,
                 "Maximum" = attributes(data_tidy)$maximum,
                 "NAs" = attributes(data_tidy)$na_count))

```

